The \dealii Library, Version 9.0

### 2018-05-20 9.0/paper.tex
fix my affiliation

T.~Heister was partially supported by the Computational Infrastructure in
Geodynamics initiative (CIG), through the National Science Foundation (NSF)
under Award No. EAR-0949446 and EAR-1550901 and The University of
California -- Davis, and NSF Grant DMS-1522191.

>>>>

T.~Heister was partially supported by NSF Award DMS-1522191, by the
Computational Infrastructure in Geodynamics initiative (CIG), through the NSF
under Award EAR-0949446 and EAR-1550901 and The University of California --
Davis, and by Technical Data Analysis, Inc. through US Navy SBIR N16A-T003.
